---
title: "Project"
author: "LF"
subtitle: "Investigation into Chicago taxis"
echo: false
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

## Packages

```{r}
#| warning: false
#| message: false
library(tidyverse)
library(tidymodels)
library(scales)
```

```{r}
glimpse(taxi)
```

`tip` \| Whether the rider left a tip. A factor with levels "yes" and "no"\
`distance` \| The trip distance, in odometer miles\
`company` \| The taxi company, as a factor. Companies that occurred few times were binned as "other" \
`Time` \| time of requested loan \
`local` \| Whether the trip's starting and ending locations are in the same community. See the source data for community area values\
`dow` \| The day of the week in which the trip began, as a factor\
`month` \| The month in which the trip began, as a factor \
`hour` \| The hour of the day in which the trip began, as a numeric\|

## Question 1

Is there there a relationship between the distance (in miles) someone travels in a taxi and if they tip or not?

```{r}



```

## Question 2

Do taxi passengers tend to tip more for the company Chicago Independents than the other companies

## Your own question
